---
title: "R Notebook"
output: html_notebook
---
```{r}
turtle_data_1 <- read.csv ( file ='SDB_report_2019-06-04_v1.csv', header = T)
library(tidyverse)
turtle_data_1 %>% filter(SCL<60) %>% count(Turtle_ID)
turtle_data_1 %>% mutate(Size.Class = if_else(SCL > 90, 3, 
                                                 if_else(SCL <= 90 & SCL > 60, 2, 1))) -> turtle_data2
str(turtle_data2)

```
Need to create a date column, then start sorting size classes between years to create some histograms of number of turtles per size group per year. 
Could also look at number of turtles in small size class each year, and then look at what breeding area they are coming from to see where most new recruits are coming from?

```{r}
turtle_data2 %>% group_by(Turtle_ID) %>% 
  summarize(meanSCL = mean(SCL, na.rm=T), 
            meanMass = mean(Weight, na.rm = T), 
            firstSCL = first(SCL), 
            firstMass = first(Weight),
            lastSCL = last(SCL), 
            lastMass = last(Weight),
            firstDate = first(Yr), 
            lastDate = last(Yr)) -> stats_size_data
data.frame(stats_size_data)
```
Historgrams of sizes for five year chunks
```{r}
Years_1990_1995 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <= 1995)
hist(Years_1990_1995$Size.Class)

Years_1996_2000 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <= 2000) %>% filter(Yr >= 1996)
hist(Years_1996_2000$Size.Class)

Years_2001_2005 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <= 2005) %>% filter(Yr >= 2001)
hist(Years_2001_2005$Size.Class)

Years_2006_2010 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <= 2010) %>% filter(Yr >= 2006)
hist(Years_2006_2010$Size.Class)

Years_2011_2015 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <= 2015) %>% filter(Yr >= 2011)
hist(Years_2011_2015$Size.Class)

Years_2016_2019 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr >= 2016)
hist(Years_2016_2019$Size.Class)


```
Need to find a way to not count multiple captures of same turtle in same year?
Break down the 2000s more, maybe year by year.
Turtles moving up size classes or are more medium size turtles coming into the bay?
Might be more helpful to look at percentages of turtles in each size class in each year to account for different amounts of captures each year, could also be easier to filter out multiple captures
Looking at every two years would also even out the adult turtles leaving for breeding on a bi-annual basis
```{r}
turtle_data2 %>% group_by(Yr) %>% count(Turtle_ID) 
turtle_data2 %>% group_by(Yr) %>% count(Size.Class) -> Total_size_perYear
turtle_data2 %>% count(Yr) -> Total_perYear
data.frame(Total_perYear)
data.frame(Total_size_perYear)
```
```{r}
library(ggplot2)
#Combined histogram for turtle data from 1990-1999 due to low number of captures and complete data
Y1990_99 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr <=1999)
qplot(Y1990_99$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "1990-1999 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

#size distributions for turtles in the past 10 years
Y2018_19 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr >= 2018)
qplot(Y2018_19$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2018-19 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2017 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr == 2017)
qplot(Y2017$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2017 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black"))

Y2016 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr == 2016)
qplot(Y2016$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2016 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2015 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr == 2015)
qplot(Y2015$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2015 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2014 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr == 2014)
qplot(Y2014$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2014 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2012_13 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter(Yr >= 2012) %>% filter(Yr <= 2013)
qplot(Y2012_13$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2012-13 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2011 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter (Yr == 2011)
qplot(Y2011$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2011 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )

Y2010 <- turtle_data2 %>% group_by(Turtle_ID) %>% filter (Yr ==2010)
qplot(Y2010$Size.Class, 
      geom="histogram",
      binwidth = 1,
      main = "2010 Size Distribution",
      xlab="Size Class",
      fill=I("cadetblue3"),
      col=I("black")
      )
```

