---
title: "Functions are a bit complicated... "
output: html_notebook
---

I noticed a few things in your function NArem so here are some advice on creating functions. 

```{r}

rm(list=ls())

# You probably need to remove data/ part for this to work. 
Turtle_data3 <- read.csv( file ='data/SDB_report_2019-06-04_v3.csv', header = T)

# extract rows with NAs in SCL
tmp1 <- Turtle_data3[is.na(Turtle_data3$SCL),]
summary(tmp1)


```

When using this function first, you will get an error:

```{r}

# this is your function - I added carriage returns to make them easier to read
NArem <- function(x) {
  Clean_data$SCL2 <- ifelse(!is.na(x$SCL), 
                            x$SCL2 <- x$SCL, 
                            ifelse(is.na(x$SCL) & !is.na(x$CCL), 
                                   x$SCL2 <- (x$CCL-0.64)/1.06,
                                   ifelse(is.na(x$SCL) & is.na(x$CCL) & !is.na(x$Weight), 
                                          x$SCL2 <- (log(x$Weight)-0.94)/0.04, 
                                          x$SCL2 <- NA)))
  
  return(data.frame(Clean_data)) 
}


NArem(tmp1)
```

This is because "Clean_data" does not exist in your function. It's best to have everything contained within each function so that the function can be used elsewhere. 

So, I will fix that part first. Notice I changed the returning dataframe also:

```{r}
NArem <- function(x) {
  x$SCL2 <- ifelse(!is.na(x$SCL), 
                   x$SCL2 <- x$SCL, 
                   ifelse(is.na(x$SCL) & !is.na(x$CCL), 
                          x$SCL2 <- (x$CCL-0.64)/1.06,
                          ifelse(is.na(x$SCL) & is.na(x$CCL) & !is.na(x$Weight), 
                                 x$SCL2 <- (log(x$Weight)-0.94)/0.04, 
                                 x$SCL2 <- NA)))
  
  return(data.frame(x)) 
}

tmp2 <- NArem(tmp1)

tmp2 %>% select(SCL, CCL, Weight, SCL2)

```

Other thing you should fix is that you don't need <- within ifelse statements. I'm actually surprised that they worked... here is what it should look like:

```{r}
NArem <- function(x) {
  x$SCL2 <- ifelse(!is.na(x$SCL), 
                   x$SCL, 
                   ifelse(is.na(x$SCL) & !is.na(x$CCL), 
                          (x$CCL-0.64)/1.06,
                          ifelse(is.na(x$SCL) & is.na(x$CCL) & !is.na(x$Weight), 
                                 (log(x$Weight)-0.94)/0.04, 
                                 NA)))
  
  return(x)
}
  
```

I also removed data.frame() at the end because x should be a dataframe to begin with. 

```{r}

tmp2 <- NArem(tmp1)
tmp2 %>% select(SCL, CCL, Weight, SCL2)

```

That's it!

